Manuscript

### 2015-03-18 inst/simulation/manuscript.Rmd
...

pc1a <- getPopulationCorrelations(scenarios="A", modelNames=modelNames[1], cutoff=cutoff)
pc1b <- getPopulationCorrelations(scenarios="B", modelNames=modelNames[1], cutoff=cutoff)
pc1c <- getPopulationCorrelations(scenarios="C", modelNames=modelNames[1], cutoff=cutoff)
pc1d <- getPopulationCorrelations(scenarios="D", modelNames=modelNames[1], cutoff=cutoff)
pc1e <- getPopulationCorrelations(scenarios="E", modelNames=modelNames[1], cutoff=cutoff)
pc1f <- getPopulationCorrelations(scenarios="F", modelNames=modelNames[1], cutoff=cutoff)
pc1 <- rbind(pc1a,pc1b,pc1c,pc1d,pc1e,pc1f)
pc2a <- getPopulationCorrelations(scenarios="Acombined", modelNames=modelNames[1], cutoff=10*cutoff)
pc2b <- getPopulationCorrelations(scenarios="Bcombined", modelNames=modelNames[1], cutoff=10*cutoff)
pc2c <- getPopulationCorrelations(scenarios="Ccombined", modelNames=modelNames[1], cutoff=10*cutoff)
pc2d <- getPopulationCorrelations(scenarios="Dcombined", modelNames=modelNames[1], cutoff=10*cutoff)
pc2e <- getPopulationCorrelations(scenarios="Ecombined", modelNames=modelNames[1], cutoff=10*cutoff)
pc2f <- getPopulationCorrelations(scenarios="Fcombined", modelNames=modelNames[1], cutoff=10*cutoff)
pc2 <- rbind(pc2a,pc2b,pc2c,pc2d,pc2e,pc2f)
pc3 <- getPopulationCorrelations(scenarios=paste0(scenarios, "10days"), modelNames=modelNames[1], cutoff=cutoff)

>>>>

pc1a <- getPopulationCorrelations(scenarios="A", modelNames=modelNames[1], cutoff=cutoff)
pc1b <- getPopulationCorrelations(scenarios="B", modelNames=modelNames[1], cutoff=cutoff)
pc1c <- getPopulationCorrelations(scenarios="C", modelNames=modelNames[1], cutoff=cutoff)
pc1d <- getPopulationCorrelations(scenarios="D", modelNames=modelNames[1], cutoff=cutoff)
pc1e <- getPopulationCorrelations(scenarios="E", modelNames=modelNames[1], cutoff=cutoff)
pc1f <- getPopulationCorrelations(scenarios="F", modelNames=modelNames[1], cutoff=cutoff)
pc1 <- rbind(pc1a,pc1b,pc1c,pc1d,pc1e,pc1f)
pc2a <- getPopulationCorrelations(scenarios="Acombined", modelNames=modelNames[1], cutoff=10*cutoff)
pc2b <- getPopulationCorrelations(scenarios="Bcombined", modelNames=modelNames[1], cutoff=10*cutoff)
pc2c <- getPopulationCorrelations(scenarios="Ccombined", modelNames=modelNames[1], cutoff=10*cutoff)
pc2d <- getPopulationCorrelations(scenarios="Dcombined", modelNames=modelNames[1], cutoff=10*cutoff)
pc2e <- getPopulationCorrelations(scenarios="Ecombined", modelNames=modelNames[1], cutoff=10*cutoff)
pc2f <- getPopulationCorrelations(scenarios="Fcombined", modelNames=modelNames[1], cutoff=10*cutoff)
pc2 <- rbind(pc2a,pc2b,pc2c,pc2d,pc2e,pc2f)
pc3a <- getPopulationCorrelations(scenarios="A10days", modelNames=modelNames[1], cutoff=cutoff)
pc3b <- getPopulationCorrelations(scenarios="B10days", modelNames=modelNames[1], cutoff=cutoff)
pc3c <- getPopulationCorrelations(scenarios="C10days", modelNames=modelNames[1], cutoff=cutoff)
pc3d <- getPopulationCorrelations(scenarios="D10days", modelNames=modelNames[1], cutoff=cutoff)
pc3e <- getPopulationCorrelations(scenarios="E10days", modelNames=modelNames[1], cutoff=cutoff)
pc3f <- getPopulationCorrelations(scenarios="F10days", modelNames=modelNames[1], cutoff=cutoff)
pc3 <- rbind(pc3a,pc3b,pc3c,pc3d,pc3e,pc3f)
#pc3 <- getPopulationCorrelations(scenarios=paste0(scenarios, "10days"), modelNames=modelNames[1], cutoff=cutoff)
